

\section*{Acknowledgements}
Firstly, I want to express my sincere gratitude to all members of the  `model development'-group at `Zentralanstalt f\"ur Meteorologie und Geodynamik' and in particular to my scientific supervisor Dr. Clemens Wastl. Everyone in the department  was incredibly patient, especially with my initial lack of knowledge in meteorology, offering insightful explanations and great support. \\
Florian Weidle and Florian Meier helped me a lot to get on with the peculiarities of using the high performance computer at the ECMWF and Josef Kemetmüller was never tired of demystifying the underlying mathematics of the model for me. Moreover, I am grateful to have had the opportunity to profit from Jasmin Vural's experience and her advice on scientific writing. Thanks to them, but also to Christoph Wittmann and Clemens Wastl, I felt welcome at the department from day one.\\
Dr. Wastl's door was always open and he helped me to stay on track during my research phase, without interfering too much, letting me create a work based on my own ideas.\\ \\
I would also like to acknowledge Prof. Roland Netz at Free University of Berlin and Mag. Christoph Wittmann and Dr. Yong Wang at ZAMG for making this cooperation possible and letting me carry out this thesis in the form as it is.\\ \\
Finally, I want to thank my family for their support throughout my studies, especially my brother Andreas Haselsteiner. He was not only always willing to discuss the topics of my research, but also to help in times of struggle of more personal nature.\\
Special thanks goes to all my dear friends, in particular to Clemens Heistracher and Christa Lichtenberger, who have always been a source of encouragement, even when being on the other side of the globe.
Without you, my studies, including working on this thesis, wouldn't have been half as much fun and as successful, thanks to our shared studying sessions and the sometimes badly needed distractions.
